\tit

### 2021-03-01 paper.tex
wording

\item \citet{FirsovUustalu2013} used Agda to formalize regular expressions with a corresponding inductive type of language membership proofs and then related regular expressions to nondeterministic finite automata (NFAs) represented as boolean matrices, as well as operations on that representation that correspond to those on regular expressions.
They then proved soundness and completeness of the NFA representation with respect to regular language membership.

>>>>

\item \citet{FirsovUustalu2013} formalized regular expressions in Agda with a corresponding inductive type of language membership proofs and related regular expressions to nondeterministic finite automata (NFAs) represented as boolean matrices.
They also defined operations on that representation corresponding to those on regular expressions and proved soundness and completeness of the NFA representation with respect to regular language membership.
